Preregistration analysis, Cost 2 study

### 2019-05-09 Cost2/Cost2_prereg.Rmd
slight changes to plot size and width of error bars

``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# prep data to plot the p(accept) based on reward, handling time and cost type
trueProp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Reward, optimal) %>%
        summarise(pComplete = mean(Choice)) %>%
        group_by(Cost, Handling, Reward, optimal) %>%
        summarise(meanComplete = mean(pComplete),
                  SE = sd(pComplete) / sqrt(length(pComplete)))

>>>>

``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 4}
# prep data to plot the p(accept) based on reward, handling time and cost type
trueProp <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Reward, optimal) %>%
        summarise(pComplete = mean(Choice)) %>%
        group_by(Cost, Handling, Reward, optimal) %>%
        summarise(meanComplete = mean(pComplete),
                  SE = sd(pComplete) / sqrt(length(pComplete)))
